Intersection of non-matching grids of different dimensions

### 2016-09-21 paper_intersections.tex
Add general description of prolongation logic.

A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:

\begin{itemize}
    \item \textbf{IP lies at 1D element node and inside 3D element} \\
            We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
    \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
            We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
            push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
            If the candidates pair has been investigated already, we skip it.
    \item \textbf{IP lies inside 1D element node (therefore must be on the surface of 3D element)} \\
            The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
            there is no 1D neighbor.
\end{itemize}

>>>>

% A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:

% \begin{itemize}
%     \item \textbf{IP lies at 1D element node and inside 3D element} \\
%             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
%     \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
%             We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
%             or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
%             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
%             If the candidates pair has been investigated already, we skip it.
%     \item \textbf{IP lies inside 1D element (therefore must be on the surface of 3D element)} \\
%             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
%             there is no 1D neighbor.
% \end{itemize}

A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
\begin{itemize}
    \item \textbf{IP lies on component element side and inside bulk element} \\
            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
            We find the component neighboring elements over the sides and push a new candidate pair
            [component neighbor -- current bulk element] into component queue.
    \item \textbf{IP lies on component element side and on the surface of bulk element} \\
            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
            push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
            If the candidates pair has been investigated already, we skip it.
    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
            The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
            there is no component neighbor.
\end{itemize}

% 2d-3d prolongation logic CURRENT
% IP is:
% - inside 2D element side
%     - inside 3D element
%         - get the neighboring 2D elements over the side
%         - push to component queue candidates pair [2D neigbor -- current 3D element]
% - inside the face of 3D element
%     - get the neighboring 3D element over the face
%     - push to bulk queue candidate pair [2D neighbor -- 3D element]
% 
% 2d-3d prolongation logic WITH FUTURE CORRECTIONS
% IP is:
% - on 2D element side
%     - find 2D element sides (if at node) and the corresponding neighbors
%     - inside 3D element
%         - push to component queue candidates pairs [2D neigbor -- current 3D element]
%     - on the surface of 3D element
%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%         - get the 3D neighbors over the faces
%         - push to bulk queue new candidates pairs
%             - [current 2D element -- 3D neighbor]
%             - [2D neighbor -- 3D neighbor] (all combinations)
%             - check whether the candidate pair has not been computed yet
% - inside the 2D element (=> on the surface of 3D element)
%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%     - get the 3D neighbors over the faces
%     - push to bulk queue new candidates pairs [current 2D element -- 3D neighbor]
%     - check whether the candidate pair has not been computed yet
